Reasoning Graphically about Quantum Computation

### 2008-02-24 papers/reasoning-graphically/paper.tex
some stuff, added picture
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1353 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann,ursula.barth,ingrid.beyer,natalie.brecht,|
\urldef{\mailsb}\path|christine.guenther,frank.holzwarth,piamaria.karbach,|
\urldef{\mailsc}\path|anna.kramer,erika.siebert-cole,lncs}@springer.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{University of Edinburgh \and
University of Oxford
%\mailsa\\
%\mailsb\\
%\mailsc
}

@@

\noindent Such pictures represent an infinite family of concrete
graphs. In this section we describe an extension of the representation
for Compact Closed Categories that allows a graph-based representation
that captures an infinite family of graphs. Notably, this allows us to
represent laws about quantum computation, such as
Spider-Law~\ref{spider-law-fig}. Furthermore, this representation is
still compositional in the sense that we can compose graphs. The
extension, which we call \ref{graph patterns}, adds two extra kinds of
nodes to the graph: {\em banged nodes} which informally represent an
arbitrary number of copies of that node, and {\em variable nodes}
which informally represent some as yet unkown node in a graph.

\subsection{Banged Nodes}

@@

@@

\section{Graph Rewriting}
\label{sec:rewriting}

\subsection{Rules}
\subsection{Matching}
\subsection{Substitution}

@@

>>>>

\usepackage{url}
\urldef{\mailsa}\path|l.dixon@ed.ac.uk|
\urldef{\mailsb}\path|ross.duncan@comlab.ox.ac.uk|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\mailsa, University of Edinburgh
\and \mailsb, University of Oxford
%\mailsa\\
%\mailsb\\
%\mailsc
}

@@

\noindent Such pictures represent an infinite family of concrete
graphs. In this section we describe an extension of the representation
for Compact Closed Categories that allows a graph-based representation
that captures an infinite family of graphs. Notably, this allows us to
represent laws about quantum computation, such as
Spider-Law~\ref{spider-law-fig}. Furthermore, this representation is
still compositional in the sense that we can compose graphs. The
extension, which we call \ref{graph patterns}, adds two extra kinds of
nodes to the graph. Namely, {\em banged boxes} which informally
represent an arbitrary number of copies of a node (where the node is
defined as some graph), and {\em variable nodes} which informally
represent some, as yet unkown, node in a graph.

\subsection{Bang-Boxes}

Bang-Boxes

@@

In graph patterns, variable nodes generalise the concept of a
half-edge. A graph with variable nodes is given the following
interpretation in the underyling semantics of our concrete graphs:

Definition: super-type: given a node with type T

\begin{itemize}
\item let the node kinds be denoted by the set $K$
\item given a graph $G$ containing a set of variable nodes $V$ 
  a given node $n$, it's type is written $T_n$,
\end{itemize}

@@

\subsection{Instantiation}

\section{Graph Pattern Rewriting}
\label{sec:rewriting}

\subsection{Rules}
\subsection{Unification}
\subsection{Substitution}

\section{Node Expressions}
\label{sec:node-expressions}

@@

Initially one might be tempted to think that the usual notion of
subgraph might surfice for expressing matching, however it allows
additional edges on nodes where, because of the tensorial semantics of
our graphs, we do not. Our work provides a restriction of the usual
subgraph definition that is sound for Compact Closed Categories.

Link Graphs and their extention to BiGraphs also encapsualte a very
different kind of semantics where they allow edges to go to multiple
nodes. An interesting area of further work would be to consider our
graph patterns for these, and other, graph based formalisms.

Graph Grammars...

Other graph rewriting...

Matrix Based Graph Tansformation...

Other Graph Transformation...
